Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)\\ Technical Appendix Including Proofs and Details

### 2017-09-19 fully-abstract-comp/technical-report.tex
compilation issues
Added some comments about the current version of splice

\begin{align*}
  \sem{\tgetb{r_1}{r_2}}(\Phi) = & 
                                   \begin{cases}
                                     \updPcAddr{\Phi\updReg{r_1}{\baddr}} & 
                                     \arraycolsep=0tpf
                                     \begin{array}[t]{l}
                                       \Phi(r_2) = ((\_,\_),\baddr,\_,\_) \\
                                       \quad \src{\tor \Phi(r_2) = \stkptr{\_,\baddr,\_,\_} } \\
                                     \end{array} \\
                                     \updPcAddr{\Phi\updReg{r_1}{-1}} & \totherwise
                                   \end{cases}
\end{align*}

@@

\noindent\textbf{splice}\\
\begin{align*}
  \sem{\tsplice{r_1}{r_2}{r_3}} = &
                              \begin{cases}
                                \updPcAddr{}\left(
                                \arraycolsep=0pt
                                \begin{array}{r l}
                                  \Phi&\updReg{r_2}{w_2}\\
                                      &\updReg{r_3}{w_3}\\
                                      &\updReg{r_1}{c}
                                \end{array}\right)
&
                                \arraycolsep=0pt
                                \begin{array}[t]{l}
                                  \Phi(r_2) = ((\perm,\lin),\baddr_2,\eaddr_2,\aaddr_2) \tand \\
                                  \Phi(r_3) = ((\perm,\lin),\baddr_3,\eaddr_3,\aaddr_3) \tand \\
                                  \perm \neq \enter \tand \\
                                  \baddr_2 = \eaddr_3 \tand \baddr_2 \leq \eaddr2 \tand \baddr_3 \leq \eaddr_3 \tand \\
                                  c = ((\perm,\lin),\baddr_2,\eaddr_3,\aaddr_2) \\
                                  w_2 = \linCons{\Phi(r_2)} \tand \\
                                  w_3 = \linCons{\Phi(r_3)} \\
                                \end{array}\\
                                \updPcAddr{}\left(
                                \arraycolsep=0pt
                                \begin{array}{r l}
                                  \Phi&\updReg{r_2}{w_2}\\
                                      &\updReg{r_3}{w_3}\\
                                      &\updReg{r_1}{c}
                                \end{array}\right)
&
                                \arraycolsep=0pt
                                \begin{array}[t]{l}
                                  \Phi(r_2) = \seal{\lin,\sigma_{\baddr,2},\sigma_{\eaddr,2}} \tand \\
                                  \Phi(r_3) = \seal{\lin,\sigma_{\baddr,3},\sigma_{\eaddr,3}} \tand \\
                                  \sigma_{\baddr,2} = \sigma_{\eaddr,3} \tand \sigma_{\baddr,2} \leq \sigma_{\eaddr,2} \tand \sigma_{\baddr,3} \leq \sigma_{\eaddr,3} \tand \\
                                  c = \seal{\lin,\sigma_{\baddr,2},\sigma_{\eaddr,3}} \\
                                  w_2 = \linCons{\Phi(r_2)} \tand \\
                                  w_3 = \linCons{\Phi(r_3)} \\
                                \end{array}\\
                                \updPcAddr{}\left(
                                \arraycolsep=0pt
                                \begin{array}{r l}
                                  \Phi&\updReg{r_2}{0}\\
                                      &\updReg{r_3}{0}\\
                                      &\updReg{r_1}{c}
                                \end{array}\right)
&
                                \arraycolsep=0pt
                                \begin{array}[t]{l}
                                  \Phi(r_2) = \stkptr{\perm,\baddr_2,\eaddr_2,\aaddr_2} \tand \\
                                  \Phi(r_3) = \stkptr{\perm,\baddr_3,\eaddr_3,\aaddr_3} \tand \\
                                  \perm \neq \enter \tand \\
                                  \baddr_2 = \eaddr_3 \tand \baddr_2 \leq \eaddr2 \tand \baddr_3 \leq \eaddr_3 \tand \\
                                  c = \stkptr{\perm,\baddr_2,\eaddr_3,\aaddr_2} \\
                                \end{array}\\
                                \failed & \totherwise
                              \end{cases}
\end{align*}

>>>>

\begin{align*}
  \sem{\tgetb{r_1}{r_2}}(\Phi) = & 
                                   \begin{cases}
                                     \updPcAddr{\Phi\updReg{r_1}{\baddr}} & 
                                     \arraycolsep=0pt
                                     \begin{array}[t]{l}
                                       \Phi(r_2) = ((\_,\_),\baddr,\_,\_) \\
                                       \quad \src{\tor \Phi(r_2) = \stkptr{\_,\baddr,\_,\_} } \\
                                     \end{array} \\
                                     \updPcAddr{\Phi\updReg{r_1}{-1}} & \totherwise
                                   \end{cases}
\end{align*}

@@

\noindent\textbf{splice}\\
\lau{19-09-2017: Two important points about $\tsplice{}{}{}$ related to the calling convention: (1) Splice fails if two capabilities are not adjacent. This means that if a caller tries to use a return pointer with a stack that is not immediately adjacent to the private stack, then it fails. (2) Splice prohibit splicing with an empty capability! This means that a callee cannot return an empty stack (this also means that it is impossible to make a call when all of the stack is used - this may indeed be undesirable, but without this restriction we need to handle other things).}
\lau{19-09-2017: Because $\tsplice{}{}{}$ does not allow empty stacks, it is not ``left inverse'' to $\tsplit{}{}{}{}$ (because of the empty case). Intuitively, it is weird that a $\tsplit{}{}{}{}$ followed by a $\tsplice{}{}{}$ does not yeild the same capability.}
  \sem{\tsplice{r_1}{r_2}{r_3}} = &
                                \updPcAddr{}\left(
                                \begin{array}{r l}
                                  \Phi&\updReg{r_2}{w_2}\\
                                      &\updReg{r_3}{w_3}\\
                                      &\updReg{r_1}{c}
                                \end{array}\right)
&
                                  \Phi(r_2) = ((\perm,\lin),\baddr_2,\eaddr_2,\aaddr_2) \tand \\
                                  \Phi(r_3) = ((\perm,\lin),\baddr_3,\eaddr_3,\aaddr_3) \tand \\
                                  \perm \neq \enter \tand \\
                                  \eaddr_2 + 1 = \baddr_3 \tand \baddr_2 \leq \eaddr_2 \tand \baddr_3 \leq \eaddr_3 \tand \\
                                  c = ((\perm,\lin),\baddr_2,\eaddr_3,\aaddr_2) \\
                                  w_2 = \linCons{\Phi(r_2)} \tand \\
                                  w_3 = \linCons{\Phi(r_3)} \\
                                \updPcAddr{}\left(
                                \begin{array}{r l}
                                  \Phi&\updReg{r_2}{w_2}\\
                                      &\updReg{r_3}{w_3}\\
                                      &\updReg{r_1}{c}
                                \end{array}\right)
&
                                  \Phi(r_2) = \seal{\lin,\sigma_{\baddr,2},\sigma_{\eaddr,2}} \tand \\
                                  \Phi(r_3) = \seal{\lin,\sigma_{\baddr,3},\sigma_{\eaddr,3}} \tand \\
                                  \sigma_{\baddr,2} = \sigma_{\eaddr,3} \tand \sigma_{\baddr,2} \leq \sigma_{\eaddr,2} \tand \sigma_{\baddr,3} \leq \sigma_{\eaddr,3} \tand \\
                                  c = \seal{\lin,\sigma_{\baddr,2},\sigma_{\eaddr,3}} \\
                                  w_2 = \linCons{\Phi(r_2)} \tand \\
                                  w_3 = \linCons{\Phi(r_3)} \\
                                \updPcAddr{}\left(
                                \begin{array}{r l}
                                  \Phi&\updReg{r_2}{0}\\
                                      &\updReg{r_3}{0}\\
                                      &\updReg{r_1}{c}
                                \end{array}\right)
&
                                  \Phi(r_2) = \stkptr{\perm,\baddr_2,\eaddr_2,\aaddr_2} \tand \\
                                  \Phi(r_3) = \stkptr{\perm,\baddr_3,\eaddr_3,\aaddr_3} \tand \\
                                  \perm \neq \enter \tand \\
                                  \baddr_2 = \eaddr_3 \tand \baddr_2 \leq \eaddr2 \tand \baddr_3 \leq \eaddr_3 \tand \\
                                  c = \stkptr{\perm,\baddr_2,\eaddr_3,\aaddr_2} \\
